Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-11-18 awipev-CO2.Rmd
script updated with new path and data from NRT database

    dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 2) %>%

@@

@@

@@

<!--The slope is in days: `r at_slope_TA3` x 3600 x 24 x 365.24 = `r at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.
-->

```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# # Plot of regression
# p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
#     geom_point() + geom_smooth(method='lm', se=FALSE)+ 
#     #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
#    geom_hline(yintercept = 0, linetype="dashed" )+
#   geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
#   #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
#   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
#                      "Intercept =",signif(fit$coef[[1]],5 ),
#                      " Slope =",signif(fit$coef[[2]], 5),
#                      " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
#   scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
# print(p)
# ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
# ```

@@

```
<!--For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
-->

#### **Final TA corrected data (Regression)**

@@

```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
# d_all_at_discrete <- d_all %>% #  To remove an outlier in red 
#   dplyr::select(datetime, month,closest_datetime, at, sal_fb)%>%
#   dplyr::filter( !is.na(at) & !is.na(sal_fb) & sal_fb >30)
#   
#   #at != "2307.05" & sal_fb > 28, !is.na(at))
# 
# # d_all_Out <- d_all %>% #  To keep an outlier in red 
# #   filter(at == "2307.05")
# 
# #fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal_fb)
# fit <- lm(data = d_all_at_discrete, at ~ sal_fb)
# slope_s_at <- fit$coefficients[[2]]
# intercept_s_at <- fit$coefficients[[1]]
# # at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()
#  
# at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
#   geom_text( aes(color=factor(month))) +
#   scale_color_discrete(guide="none")+
#     labs(x="Salinity", y="Discrete AT", color = "Months")  +
#     stat_smooth(method = "lm", col = "black") +
#     labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
#                        ";\nIntercept =",signif(fit$coef[[1]],5 ),
#                        ";\nSlope =",signif(fit$coef[[2]], 5),
#                        ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
#   theme_bw() + 
#   theme(aspect.ratio=1,
#         axis.text=element_text(size=15),
#         axis.title.y= element_text(size =15),
#         axis.title.x= element_text(size =15),
#         plot.margin = unit(c(0.5,1,1,1), "cm"),
#         plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70))) 
#   #print(at_s)
# 
# ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")
# 
# # Salinity is a predictor of AT -> using the regression defined above
# d_all$at_calc <- slope_s_at * d_all$sal_fb + intercept_s_at
```
<!--The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r round(summary(fit)$r.squared, digits=2)`. Need to compare with other relationships from the literature.
-->
```{r plot Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%", fig.align="center"}
# # PLOT
# print(at_s)
```

@@

### **Corrected Contros vs calculated *p*CO~2~ data**
```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  PCO2_corr_contros ~ pco2calc , nperm = 99)

pco2calc_pCO2_contros_text <-  ggplot(d_all,aes(x=pco2calc, y= PCO2_corr_contros, label = month))+
   geom_text(aes(color = factor(month)))+
  scale_color_discrete(guide="none")+
  geom_line(aes(x = PCO2_corr_contros, y = PCO2_corr_contros), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_contros, PCO2_Corr_filtered)
pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
    dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 2) %>%
    dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
      dyEvent(as.POSIXct("2019-09-03 15:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>%

@@

# Offset between durafet pH and spec pH 
duroffset <- left_join(durPeriod[,c(1,2)], d_all[,c(1,18)], by="datetime")
dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_field - pH_durafet)
average_offset_dur <- round(mean(dat_dur$diff_pH_dur, na.rm=TRUE), digits = 2)
sd_offset_dur <- round(sd(abs(dat_dur$diff_pH_dur), na.rm=TRUE), digits = 2)
n_offset_dur <- length(!is.na(dat_dur$diff_pH_dur))

@@

```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# remove sf biofouling period
pH_sf <- d_all %>%
  dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pHint_tot_sf)%>%
  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu), !is.na(temp_fb)) %>%
  dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu, Pinsi=11, S=pH_sf$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

pH_dur <- d_all %>%
  dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pH_durafet_corrected)%>%
  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_insitu))
pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_insitu, Pinsi=11, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

# join pH calc norm + pH dur/sf norm in d_all
d_all <- left_join(d_all, pH_calc[, c(1,6)], by="datetime")

@@

### **TA analyser**
- **2019-07-12**: Steffen told us that calibration was not OK. To check it, he calculated the mediane of the pH/volume sample / volumeIndicatorfactor and compared them to January/October calibration. We wait for Steffen recommandations before to make another calibration.
- **2019-06-07**: Samir did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. TA was stable before the calibration and calibration was OK.
- **2019-02-15**: No data from 15th (14:08:21 UTC) to 19th February (14:58:46 UTC). files transfered but no data. No explanation.
- **2019-01-26**: Philipp did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. Flow filter was also lifted up and the seawater flow has therefore increased.
- **2019-01-16**: Bad data since this date. 
- **2018-12-28**: HCL and BCG cartridges were changed by Marine.
- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer). Samir received password and access from the AWI in order to communicate from France with the TA.
- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again. First data were received (high: 2450 and low: 2150) but salinity issue since this time. Uwe/Philipp try to find if this comes from comunication issue with the FB.
- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
- **2017-02-10**: TA cleaning salt crusts.
- **2017-02-09**: TA calibration with CRM at 12:20.
- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode). Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
- **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
- **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
- **2016-05-01**: No data for TA.
- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).

@@

@@

### ***p*CO~2~**
- **2018-08-29**: Calibration parameters from #0215-001 were added to "./data/Calibration_pCO2/Data_Processing_sheet_pCO2.csv".
- **2018-04-20**: For *p*CO~2~ Calibration the previous period (N° 4) was added to the script "ny-alesund_cc" line 466.
- **2015-10-13**: we put back the spike.pCO2 to 600 because data in October reached more than 350 µAtm. We let this like that and we are going to deal with it manually later if needed.
- **2015-09-28**: we put the spike.pCO2 (detection of peaks: threshold) at 350 to remove anomalies on the 12 and 15 September. We have to monitor data. If data reach this value, then problem.

@@

### **Files - server**
- **2018-04-19**: Since "Ferrybox" is on again, the adding to solve the files issues are making not data into d_hour for this period (2018-09-03 to 2018-14-04). This adding was put in comments now. In seaFET data reading, S/N have been changed from 1005 to 0007.
- **2018-03-21**: Files issues. FerryBox instruments are down because of freezing but UWO instrument as seaFET and SBE38 are OK. Removing of one 0 octet file from seaFET20180317_1404 and put back seaFET files from 20180309 to 20180312 in seaFET folder. They were in SBE38 folder...Weird. Additionnal script lines were added in order to deal with the issue of "in situ" created date whereas "Ferrybox" created data ware not. Since "in situ" parameters are running (d df) and not "in ferrybox" parameters (z df), the new datetime lines are not taking in consideration with the left_join function we have to add them during Ferrybox shutdown.
- **2018-03-09**: Script issue solved with first negative values encountred in SBE38 files. We find a regex solution to take "space + space or negative value" in consideration.
- **2017-11-07**: Wrong seaFET files (wrong datetime starting on the 5th September) from 24 to 26 October were fixed. File "SVL_20171024_030426_to_20171026_110425_SeaFet-1005.txt" were created in SeaFet_archive.

>>>>

@@

      dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%

@@

    dyEvent(as.POSIXct("2019-09-03 15:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 

@@

<!--The slope is in days: `r at_slope_TA3` x 3600 x 24 x 365.24 = `r at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.

```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# # Plot of regression
 p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
     geom_point() + geom_smooth(method='lm', se=FALSE)+ 
     #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
    geom_hline(yintercept = 0, linetype="dashed" )+
   geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
   #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                      "Intercept =",signif(fit$coef[[1]],5 ),
                      " Slope =",signif(fit$coef[[2]], 5),
                      " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
   scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
 print(p)
 ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
```

@@

```
For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
-->
<!--
#### **Final TA corrected data (Regression)**

@@

```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
# d_all_at_discrete <- d_all %>% #  To remove an outlier in red 
#   dplyr::select(datetime, month,closest_datetime, at, sal_fb)%>%
#   dplyr::filter( !is.na(at) & !is.na(sal_fb) & sal_fb >30)
#   
#   #at != "2307.05" & sal_fb > 28, !is.na(at))
# 
# # d_all_Out <- d_all %>% #  To keep an outlier in red 
# #   filter(at == "2307.05")
# 
# #fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal_fb)
# fit <- lm(data = d_all_at_discrete, at ~ sal_fb)
# slope_s_at <- fit$coefficients[[2]]
# intercept_s_at <- fit$coefficients[[1]]
# # at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()
#  
# at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
#   geom_text( aes(color=factor(month))) +
#   scale_color_discrete(guide="none")+
#     labs(x="Salinity", y="Discrete AT", color = "Months")  +
#     stat_smooth(method = "lm", col = "black") +
#     labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
#                        ";\nIntercept =",signif(fit$coef[[1]],5 ),
#                        ";\nSlope =",signif(fit$coef[[2]], 5),
#                        ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
#   theme_bw() + 
#   theme(aspect.ratio=1,
#         axis.text=element_text(size=15),
#         axis.title.y= element_text(size =15),
#         axis.title.x= element_text(size =15),
#         plot.margin = unit(c(0.5,1,1,1), "cm"),
#         plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70))) 
#   #print(at_s)
# 
# ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")
# 
# # Salinity is a predictor of AT -> using the regression defined above
# d_all$at_calc <- slope_s_at * d_all$sal_fb + intercept_s_at
```
The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r round(summary(fit)$r.squared, digits=2)`. Need to compare with other relationships from the literature.
-->
```{r plot Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%", fig.align="center"}
# # PLOT
# print(at_s)
```

@@

### **Corrected Contros vs calculated *p*CO~2~ data**
```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  pco2_contros ~ pco2calc , nperm = 99)

pco2calc_pCO2_contros_text <-  ggplot(d_all,aes(x=pco2calc, y= pco2_contros, label = month))+
   geom_text(aes(color = factor(month)))+
  scale_color_discrete(guide="none")+
  geom_line(aes(x = pco2_contros, y = pco2_contros), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_contros, PCO2_Corr_filtered)
pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
  dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
    dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2019-09-03 15:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>%

@@

# Offset between durafet pH and spec pH 
duroffset <- left_join(durPeriod%>%dplyr::select(datetime,pH_s_durafet_temp_field), d_all%>%dplyr::select(datetime,pH_durafet ), by="datetime")
dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_field - pH_durafet)
average_offset_dur <- round(mean(dat_dur$diff_pH_dur, na.rm=TRUE), digits = 2)
sd_offset_dur <- round(sd(abs(dat_dur$diff_pH_dur), na.rm=TRUE), digits = 2)
n_offset_dur <- length(!is.na(dat_dur$diff_pH_dur))

@@

```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# remove sf biofouling period
pH_sf <- d_all %>%
  dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pHint_tot_sf)%>%
  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal_fb)) %>%
  dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu, Pinsi=11, S=pH_sf$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

pH_dur <- d_all %>%
  dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pH_durafet_corrected)%>%
  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal_fb))
pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_insitu, Pinsi=11, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

@@

# join pH calc norm + pH dur/sf norm in d_all
d_all <- left_join(d_all, pH_calc%>%dplyr::select(datetime,pH_calc_norm4), by="datetime")

@@

### **TA analyser**
- **2019-11-15**: TA calibration done by Gwendall is OK but the sensore seems to have problem since 2019-10-16. Video conference is scheduled with Steffen on 2019-11-19. Maybe sample supply is defective.
- **2019-07-12**: Steffen told us that calibration was not OK. To check it, he calculated the mediane of the pH/volume sample / volumeIndicatorfactor and compared them to January/October calibration. We wait for Steffen recommandations before to make another calibration.
- **2019-06-07**: Samir did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. TA was stable before the calibration and calibration was OK.
- **2019-02-15**: No data from 15th (14:08:21 UTC) to 19th February (14:58:46 UTC). files transfered but no data. No explanation.
- **2019-01-26**: Philipp did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. Flow filter was also lifted up and the seawater flow has therefore increased.
- **2019-01-16**: Bad data since this date. 
- **2018-12-28**: HCL and BCG cartridges were changed by Marine.
- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer). Samir received password and access from the AWI in order to communicate from France with the TA.
- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again. First data were received (high: 2450 and low: 2150) but salinity issue since this time. Uwe/Philipp try to find if this comes from comunication issue with the FB.
- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
- **2017-02-10**: TA cleaning salt crusts.
- **2017-02-09**: TA calibration with CRM at 12:20.
- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode). Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
- **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
- **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
- **2016-05-01**: No data for TA.
- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).

@@

[AWI NRT database](https://dashboard.awi.de/data-xxl/overview.jsp)

@@

### ***p*CO~2~**
- **2019-11-18**: Calibration parameters from #0215-001 were added to "server.../data/NRT_data/Data_Processing_sheet_pCO2.csv" (new path).
- **2018-08-29**: Calibration parameters from #0215-001 were added to "./data/Calibration_pCO2/Data_Processing_sheet_pCO2.csv".
- **2018-04-20**: For *p*CO~2~ Calibration the previous period (N° 4) was added to the script "ny-alesund_cc" line 466.
- **2015-10-13**: we put back the spike.pCO2 to 600 because data in October reached more than 350 µAtm. We let this like that and we are going to deal with it manually later if needed.
- **2015-09-28**: we put the spike.pCO2 (detection of peaks: threshold) at 350 to remove anomalies on the 12 and 15 September. We have to monitor data. If data reach this value, then problem.

@@

### **Files - server**
- **2019-11-15**: Script including the new data downloading from the NRT AWI database is running (ny-alesund_cc.R). From this date, data are donwloaded from AWI NRT dtabase. We are waiting some setting from Philipp to have the entire dataset. Only 2018-2019 are available for the moment. New path was created in the server and pCloud/exp168 with "NRT_data" file. Please see the picture bellow.
- **2018-04-19**: Since "Ferrybox" is on again, the adding to solve the files issues are making not data into d_hour for this period (2018-09-03 to 2018-14-04). This adding was put in comments now. In seaFET data reading, S/N have been changed from 1005 to 0007.
- **2018-03-21**: Files issues. FerryBox instruments are down because of freezing but UWO instrument as seaFET and SBE38 are OK. Removing of one 0 octet file from seaFET20180317_1404 and put back seaFET files from 20180309 to 20180312 in seaFET folder. They were in SBE38 folder...Weird. Additionnal script lines were added in order to deal with the issue of "in situ" created date whereas "Ferrybox" created data ware not. Since "in situ" parameters are running (d df) and not "in ferrybox" parameters (z df), the new datetime lines are not taking in consideration with the left_join function we have to add them during Ferrybox shutdown.
- **2018-03-09**: Script issue solved with first negative values encountred in SBE38 files. We find a regex solution to take "space + space or negative value" in consideration.
- **2017-11-07**: Wrong seaFET files (wrong datetime starting on the 5th September) from 24 to 26 October were fixed. File "SVL_20171024_030426_to_20171026_110425_SeaFet-1005.txt" were created in SeaFet_archive.
